Validity of a model for a cantilever two-dimensional beam

### 2024-04-07 files/Chapter2/generalvibrationmodel.tex
galerkin Timo
review exam report

In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS19}. In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems. The problems in Chapter 1 are examples. The article \cite{VV02} concerns the case of a symmetric bilinear form $b$. The article \cite{VS19} extends this work where $b$ need not be symmetric. The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.

@@

Define a function u with domain $J$, an interval of real numbers. The range of $u$ is contained in $X$:
\begin{eqnarray}
	u(t)(x) = \langle w(x,t), \phi(x,t) \rangle \label{def_of_u}
\end{eqnarray}

@@

The space X with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.

@@

As mentioned before, ideas and notation from \cite{VS19} are also used.

@@

This general variational form is applicable in all the models in this dissertation. In \cite{VV02}, a more general form is given that includes the possibility for damping terms in the models. Damping is not considered in this dissertation.

@@

As mentioned, in the models of this dissertation, the bilinear form $a$ is identically zero. This automatically satisfy the weak damping condition and hence Theorem 2 may be applied.

@@

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$. So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero}

Consider \textbf{Assumption A2}. From the definition of the bilinear form $c$,
\begin{eqnarray*}
	c(f,f) & = & \int_0^1  (f_1)^2 + \frac{1}{\alpha}\int_0^1  (f_2)^2 = ||f_1||^2 + \frac{1}{\alpha}||f_2||^2.\\
\end{eqnarray*}
From this, the following inequalities can be obtained:
\begin{eqnarray*}
	\min\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2 \leq	c(f,f)	\leq \max\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2.\\
\end{eqnarray*}

@@

Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}:
\begin{eqnarray}
	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
\end{eqnarray}
with boundary conditions
\begin{eqnarray*} 
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
\begin{eqnarray*}
	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
\end{eqnarray*}
Dividing by $T(t)$,
\begin{eqnarray*}
	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
\end{eqnarray*}

@@

To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in R$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions does indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (and consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$. \label{sym:lambda}

@@

Following these results from \cite{CVV18}, for any $u \in V$, $\displaystyle u = \sum_{i=1}^{\infty} a_i x_i$. These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the eigenvectors $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i.
\end{eqnarray*}

@@

In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by \label{sym:Energy}
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

@@

Therfore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.

@@

In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string. Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions. A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.

>>>>

In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS18}. In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems. The problems in Chapter 1 are examples. The article \cite{VV02} concerns the case of a symmetric bilinear form $b$. The article \cite{VS18} extends this work where $b$ need not be symmetric. The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS18} is only used where the notation is more convenient and to gain more insight.

@@

Define a function u with domain $J$, an interval of real numbers. The range of $u$ is contained in $X$:
\begin{eqnarray}
	u(t)(x) = \langle w(x,t), \phi(x,t) \rangle. \label{def_of_u}
\end{eqnarray}

@@

The space X equipped with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.

@@

As mentioned before, ideas and notation from \cite{VS18} are also used.

@@

This general variational form is applicable to all the models in this dissertation. In \cite{VV02}, a more general form is given that includes the possibility for damping terms in the models. Damping is not considered in this dissertation.

@@

As mentioned, in the models of this dissertation, the bilinear form $a$ is identically zero. This automatically satisfies the weak damping condition and hence Theorem 2 may be applied.

@@

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$. So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L^2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L^2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L^2(0,1) \times L^2(0,1)$.\label{sym:Cinftyzero}

Consider \textbf{Assumption A2}. From the definition of the bilinear form $c$,
\begin{eqnarray*}
	c(f,f) & = & \int_0^1  (f_1)^2 + \frac{1}{\alpha}\int_0^1  (f_2)^2 = ||f_1||^2 + \frac{1}{\alpha}||f_2||^2.\\
\end{eqnarray*}
From this and the definition of the $X$ norm, the following inequalities can be obtained:
\begin{eqnarray*}
	\min\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2 \leq	c(f,f)	\leq \max\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2.\\
\end{eqnarray*}

@@

Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion2D}:
\begin{eqnarray}
	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
\end{eqnarray}
with boundary conditions
\begin{eqnarray*} 
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
\begin{eqnarray*}
	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
\end{eqnarray*}
Dividing by $T(t)$,
\begin{eqnarray*}
	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
\end{eqnarray*}

@@

To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in R$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}, \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

@@

Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
\end{eqnarray*} 
Substitution show that these solutions do indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions. These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (and consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
\end{eqnarray*} for each $\langle v, \ \psi\rangle \in T[0,1]$. \label{sym:lambda}

@@

Following these results from \cite{CVV18}, for any $u \in V$, $\displaystyle u = \sum_{i=1}^{\infty} a_i x_i$. These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the eigenvectors $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i = \sum_{i=1}^{\infty} c(u, x_i)x_i.
\end{eqnarray*}

@@

In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ of the function $u$ given by \label{sym:Energy}
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

@@

Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.

@@

In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string. Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions. A comparison of the exact solutions is not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.

### 2024-04-07 files/Chapter3/dynamicconvergence.tex
chapter 3
Chapter 3 final
submition
review exam report

Consider a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i$. The subset of these functions that satisfies the boundary conditions are called admissible basis functions. For Problem 2-T, the admissible basis functions are ${\delta_i}$ for $i = 1,2,...,n$. Define the space $S^h$ as the space spanned by the admissible basis functions, i.e.
\begin{eqnarray*}
	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
\end{eqnarray*}

@@

\subsubsection{Problem T-2V$^h$}
Find a function $u_h \in S^h\times S^h$ such that for all $t \in [0,1]$,
\begin{eqnarray*}
	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
\end{eqnarray*} for each $v \in S^h\times S^h$, where $u_h = ( w^h, \phi^h )$. $Q^I$ is a vector with elements $Q(x^*_i)$ for $i = 0,1,2,...,n$.

@@

Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists a unique solution for Problem GVar$^h$. The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.

@@

From Theorem 2 for the semi-discrete problem an error estimate for
$e(t) = [u(t)-u_h(t)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.

@@

Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
should also be with respect to the norm of $W$. The local error $e_1$ can be estimated using Taylor polynomials, but then $e_k$ `grows' as $k$ increases.

@@

Using this lemma, \cite{BV13} prove the error estimate. The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.

\newtheorem*{DC_Thm5_1}{Theorem 3}
\begin{DC_Thm5_1}
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5_1}

>>>>

Consider a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i$. The subset of these functions that satisfies the boundary conditions are called admissible basis functions. For Problem 2-T, the admissible basis functions are ${\delta_i}$ for $i = 1,2,...,n$. Define the space $S^h$ as the space spanned by the admissible basis functions, i.e.
\begin{eqnarray*}
	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
\end{eqnarray*} \label{sym:span}

@@

\subsubsection{Problem T-2V$^h$}
Find a function $u_h \in S^h\times S^h$ such that for all $t \in [0,1]$,
\begin{eqnarray*}
	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
\end{eqnarray*} for each $v \in S^h\times S^h$. For each $t$, $Q^I(t)$ is the interpolant of $Q(t)$ in $S^h$.

@@

Under the assumptions \textbf{A1}-\textbf{A4} of Chapter 2 and continuity of $f$, there exists a unique solution for Problem GVar$^h$. The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.

@@

From Theorem 2 for the semi-discrete problem an error estimate for
$e(t) = u(t)-u_h(t)$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = u_h(t_k) - u^h_k$.

@@

Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $e_k = u_h(t_k) - u^h_k$
should also be with respect to the norm of $W$. The local error $e_1$ can be estimated using Taylor polynomials, but then $e_k$ `grows' as $k$ increases.

@@

Using this lemma, \cite{BV13} prove the error estimate. The error estimate for the term $u_h(t_k) - u^h_k$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.

\newtheorem*{DC_Thm5_1}{Theorem 3}
\begin{DC_Thm5_1}
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u_h(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5_1}

### 2024-04-07 files/Chapter3/femconvergence.tex
review exam report

Problem $E^h$ can be written as a matrix eigenvalue problem,
\begin{eqnarray}
	\lambda^nM\bar{u}_n = K\bar{u}_n. \label{eq:matrix_eigenvalue}
\end{eqnarray}

@@

The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to understand some of the theory to make the connection.

@@

\section{Estimating the eigenvalues.} \label{sec:estimating_the_eigenvalues}
In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.

@@

For the requirements of this dissertation, this can be simplified with an assumption. The assumption is that the basis of $S^h$ consists of polynomials. With this assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||_{W}$. This approximation theorem can be rewritten as
\newtheorem{Interpolation_2}{Theorem}
\begin{Interpolation_2}
	Suppose there exists an integer $k$ such that for each element
	\begin{equation*}
		s(\Pi_e) + 1 \leq k \leq r(\Pi_e) +1.
	\end{equation*}
	Then there exists a constant $C$ such that for any $u \in C^k_+(I)$,
	\begin{equation*}
		||(\Pi u)^{(m)} - u^{(m)}||_{W} \leq C h^{k-m} || u^{(k)}||_{W} \ \text{ for } m = 0,1,...,k.
	\end{equation*}
\end{Interpolation_2}
\end{document}

>>>>

Problem $E^h$ can be written as a matrix eigenvalue problem,
\begin{eqnarray}
	\lambda^hM\bar{u}_n = K\bar{u}_n. \label{eq:matrix_eigenvalue}
\end{eqnarray}

@@

The pair $(\lambda^h, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to understand some of the theory to make the connection.

@@

\section{Estimating the eigenvalues.} \label{sec:estimating_the_eigenvalues}
In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, however the proofs are expanded for greater clarity.

@@

For the requirements of this dissertation, this can be simplified with an assumption. The assumption is that the basis of $S^h$ consists of polynomials. With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||_{W}$. This approximation theorem can be rewritten as
\newtheorem{Interpolation_2}{Theorem}
\begin{Interpolation_2}
	Suppose there exists an integer $k$ such that for each element
	\begin{equation*}
		s(\Pi_e) + 1 \leq k \leq r(\Pi_e) +1.
	\end{equation*}
	Then there exists a constant $C$ such that for any $u \in C^k_+(I)$,
	\begin{equation*}
		||(\Pi u)^{(m)} - u^{(m)}||_{W} \leq C h^{k-m} || u^{(k)}||_{W} \ \text{ for } m = 0,1,...,k.
	\end{equation*}
\end{Interpolation_2}
\end{document}

### 2024-04-07 files/Chapter4/CantileverBeam.tex
review exam report

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever beam} \label{sec:Timo:Cantilever}
Consider a cantilever Timoshenko beam model (Problem T-3 as defined in section \ref{ssec:1D_Model:ModelProblems}). The eigenvalue problem of Problem T-3 is denoted by Problem T-3E. This section serves as an example of the application of the theory from [VV02].\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results the following constants:
\begin{align}
	C = & \frac{\mu(\lambda-\omega^2)}{\omega(\lambda+\mu^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda < \alpha \label{A1}\\
	C = & \frac{\omega}{\lambda - \omega^2}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda = \alpha \label{A2}\\
	C = & -\frac{\omega(\lambda-\theta^2)}{\theta(\lambda-\omega^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda > \alpha \label{A3}
\end{align}
The boundary conditions at $x = 1$ reduces the general solution to the following two-dimensional homogeneous system for each of the three cases.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever beam} \label{sec:Timo:Cantilever}
Consider a cantilever Timoshenko beam model (Problem T-3 as defined in section \ref{ssec:1D_Model:ModelProblems}). The eigenvalue problem of Problem T-3 is denoted by Problem T-3E. This section serves as an example of the application of the theory from \cite{VV06}.\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results in the following constants:
\begin{align}
	C = & \frac{\mu(\lambda-\omega^2)}{\omega(\lambda+\mu^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda < \alpha \label{A1}\\
	C = & \frac{\omega}{\lambda - \omega^2}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda = \alpha \label{A2}\\
	C = & -\frac{\omega(\lambda-\theta^2)}{\theta(\lambda-\omega^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda > \alpha \label{A3}
\end{align}
The boundary conditions at $x = 1$ reduces the general solution to the following two-dimensional homogeneous system for each of the three cases.

### 2024-04-07 files/Chapter4/FreeFreeTimo.tex
review exam report

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Free-free timoshenko beam}\label{sec:Timo:Free}
Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E. Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results the following:

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Free-free Timoshenko beam}\label{sec:Timo:Free}
Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E. Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results in the following:

### 2024-04-07 files/Chapter4/ModalAnalysisTimo.tex
table of symbols
review exam report

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this chapter, more general theory for modal analysis of te Timoshenko beam theory is discussed, as well as more examples of the application of the theory.

@@

The authors of \cite{VV06} first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}. In \cite{VV06} the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative. Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$. Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
\begin{eqnarray*}
-m^{2}e^{mx}w_{1}+me^{mx}w_{2}&=&\lambda e^{mx}w_{1},\\
-\frac{1}{\gamma}m^{2}e^{mx}w_{2}-\alpha me^{mx}w_{1}+\alpha e^{mx}w_{2}&=&\lambda e^{mx}w_{2}.
\end{eqnarray*}

@@

Let $A$ denote the coefficient matrix of \eqref{eq:Timo:SolutionEigenvalueProblem}. For a nontrivial solution of $\bar{w}$, it is required that the determinant of matrix $A$ is $0$.
\begin{align*}
\textrm{det}(A)=m^{4}+\lambda(1+\gamma)m^{2}+\gamma\lambda(\lambda-\alpha)=0. \label{TE7}
\end{align*}

@@

The authors of \cite{VV06} provide a detailed example of the application of the above strategy to for determining the eigenvalues and eigenvectors. The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.

@@

The frequency equation has infinitely many solutions. Each of the solutions corresponds to a eigenvalue with a unique vector $\bar{b}$. The eigefunctions can then be obtained by substituting the vector $\bar{b}$ into the general solution for $u$ and $\phi$.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
An example of modal analysis of a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}. In this chapter, more general theory for modal analysis of the Timoshenko beam theory is discussed, as well as more examples of the application of the theory.

@@

The authors of \cite{VV06} first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}. In \cite{VV06} the authors show that for the Timoshenko models in this dissertation that $\lambda$ is non-negative. Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in R$ or $m\in C$. Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
\begin{eqnarray*}
-m^{2}e^{mx}w_{1}+me^{mx}w_{2}&=&\lambda e^{mx}w_{1},\\
-\frac{1}{\gamma}m^{2}e^{mx}w_{2}-\alpha me^{mx}w_{1}+\alpha e^{mx}w_{2}&=&\lambda e^{mx}w_{2}.
\end{eqnarray*}

@@

Let $A$ denote the coefficient matrix of \eqref{eq:Timo:SolutionEigenvalueProblem}. For a nontrivial solution $\bar{w}$, it is required that the determinant of matrix $A$ is $0$.
\begin{align*}
\textrm{det}(A)=m^{4}+\lambda(1+\gamma)m^{2}+\gamma\lambda(\lambda-\alpha)=0. \label{TE7}
\end{align*} \label{sym:determinant}

@@

The authors of \cite{VV06} provide a detailed example of the application of the above strategy for determining the eigenvalues and eigenvectors. The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.

@@

The frequency equation has infinitely many solutions. Each of the solutions corresponds to a eigenvalue with a unique vector $\bar{b}$. The eigenfunctions can then be obtained by substituting the vector $\bar{b}$ into the general solution for $u$ and $\phi$.
